|

### 2025-01-09 paper/manuscript.Rmd
reworking with ABC.

[^thanks]: We thank the participants of the *Worldview Lab at Kenan Institute for Ethics* at Duke University for their insightful and helpful comments on this project.
[^TK]: Department of Sociology, Duke University, `turgut.keskinturk@duke.edu`.
[^PB]: Department of Sociology, Duke University, `pablo.bello@duke.edu`.
[^SV]: Department of Sociology, Duke University, `stephen.vaisey@duke.edu`.

@@

```{=latex}
\begin{figure}[!ht]
\begin{center}
```
```{r figure7, out.width = "100%"}
knitr::include_graphics("../figures/detection.png")
```
```{=latex}
\end{center}
\caption*{Figure 7: Sensitivity and Specificity Across Case Studies}
\footnotesize{\textit{Notes:} The figure depicts the sensitivity---true positives divided by the sum of true positives and false positives---and specificity---true negatives divided by the sum of true negatives and false negatives---scores across three studies.}
\end{figure}
```

>>>>

[^thanks]: We thank the participants of the *Worldview Lab at Kenan Institute for Ethics* at Duke University for their insightful and helpful comments on this project.
[^TK]: Department of Sociology, Duke University, `turgut.keskinturk@duke.edu`.
[^PB]: Department of Sociology, Duke University, `pablo.bello@duke.edu`.
[^SV]: Department of Sociology and Political Science, Duke University, `stephen.vaisey@duke.edu`.

@@
